

```{r global_options, include=FALSE}

knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

CAR EDA by Ahmet Hamza Emra
========================================================
Over 370000 used cars scraped with Scrapy from Ebay-Kleinanzeigen. The content of the data is in german, so one has to translate it first if one can not speak german. Those fields are included:

dateCrawled : when this ad was first crawled, all field-values are taken from this date

name : "name" of the car

seller : private or dealer

offerType

price : the price on the ad to sell the car (Currency is EURO aloms 1Euro = 1.06Dollar)

abtest

vehicleType

yearOfRegistration : at which year the car was first registered

gearbox

powerPS : power of the car in PS (mesurement is horsepower (4500 kilometer per munite))

model

kilometer : how many kilometers the car has driven (1 kilometer = 0.621371 Mile)

monthOfRegistration : at which month the car was first registered

fuelType

brand

notRepairedDamage : if the car has a damage which is not repaired yet

dateCreated : the date for which the ad at ebay was created

nrOfPictures : number of pictures in the ad

postalCode

lastSeenOnline : when the crawler saw this ad last online


```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.






# load the ggplot graphics package and the others
library(ggplot2)
library(GGally)
library(scales)
library(memisc)
library(ggthemes)
library(RColorBrewer)
library(data.table)
library(lubridate)
library(data.table)


```

```{r echo=FALSE, Load_the_Data}
# Load the Data
data<-read.csv("autos.csv")

str(data)


```


## Formating the data
```{r}
data$nrOfPictures <- NULL 
data$seller <- NULL
data$offerType <- NULL
data<-subset(data, powerPS<1000)
data$dateCrawled <- ymd_hms(data$dateCrawled)
data$dateCreated <- ymd_hms(data$dateCreated)
data$lastSeen <- ymd_hms(data$lastSeen)
data$dateCrawled<-NULL
data$name<- NULL
data$abtest<-NULL
data$notRepairedDamage<-NULL
data$dateCreated<-NULL
data$postalCode<-NULL
data$monthOfRegistration<-NULL
data$lastSeen<-NULL

```







```{r}
summary(data)
```



# Univariate Plots Section


## Price 


```{r}
summary(data$price)
```



<p>
as we can see there are a lot of outliers for example, there should not be any car for free and also the upper band is very high. So we need to clean some data.
<p/>
```{r}

data<-subset(data,(price > quantile(data$price, 0.05)) & (price < quantile(data$price, 0.95)))
```


```{r}
summary(data$price)
```



```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x=price),data=data)+
  geom_histogram()+
  labs(title='Price Diagram', y = 'number of cars', x='Price')
  

```
```{r}
ggplot(aes(x=price),data=data)+
  geom_histogram()+
  scale_x_log10(breaks=c(1, 10, 1000, 4000, 15000, 100000), labels=comma)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```




## Year of Registration

```{r}
summary(data$yearOfRegistration)
```
also for this column max date can not be after 2016. this is which year data from. also first car ivented at 1885 (whick is still to less but), so there cannot be any thing before that year.

```{r}
data<-subset(data, yearOfRegistration<2016)
data<-subset(data, yearOfRegistration>1950)

```
after cleaning process:
```{r}
summary(data$yearOfRegistration)
```
lets create the histograms:
```{r}
ggplot(data=data,aes(x=yearOfRegistration))+
  geom_histogram()+
  labs(title='Year Of Registration', 
       y = 'number of cars', 
       x='Registration year')
  
```


```{r}
summary(data$vehicleType)
```
```{r}
ggplot(data=subset(data, vehicleType !="") , 
       aes(x=vehicleType))+
  geom_histogram(stat = 'count')
```



I think it is stange that there are more limusine than the other kind of cars.

##powerPS

```{r}
summary(data$powerPS)
```
<p>Cleaning</p>
```{r}
data<-subset(data, data$powerPS < 500)
summary(data$powerPS)
```


```{r}
ggplot(aes(x=powerPS),data=data)+
  geom_histogram()+
  scale_x_log10(breaks=c(1, 10, 1000, 4000, 15000, 100000), labels=comma)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
```

## Brand


```{r}
summary(data$brand)
```
```{r}
ggplot(data=data,aes(x=brand))+
  geom_histogram(bins = 50,stat='count')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  labs(x='Brand of Car', 
       y='number of car',
       title = 'Brad Diagram')
```



volkswagen looks like the most popular car in the market. lets check which kind of volkswagens are in market.

```{r}
ggplot(data=subset(data, brand=="volkswagen"),
       aes(model))+geom_histogram(stat = 'count')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  coord_flip()
```

## gear box


```{r}
summary(data$gearbox)
```
```{r}
gearbox_table<-table(subset(data, gearbox!="")$gearbox)

pie(gearbox_table)
```

```{r}
ggplot(aes(x= gearbox), data=subset(data, gearbox!="")) +
  geom_bar(color='black') +
  labs(x= 'Gearbox', y='Number of Cars', title='Gearbox')
```



The number of cars with manual gearbox is higher than the automatic ones. This is not surprising considering the ages and kilometers of the second-hand cars.

## kilometer

```{r}
summary(data$kilometer)
```
<p> 

```{r}
ggplot(aes(data$kilometer), data=data) +
  geom_bar(color='black', fill='orange') +
  scale_y_log10()+
  labs(x='Kilometer', 
       y='number of car',
       title = 'Kilometer Diagram')
```
The concentration on the 100.000+ km, particularly 150.000 km, is interesting, even that scale_y_log10() becomes necessary to observe the distribution.


## Fueltype

```{r}
summary(data$fuelType)
```
<br />
there are a lot of missing data in this column so we need to use subset 
<br />


```{r}

ggplot(data=subset(data, fuelType!=""), aes(x=fuelType))+
  geom_histogram(stat = 'count')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  labs(x='Kilometer', 
       y='number of car',
       title = 'Kilometer Diagram')


```
<br />

Majority of the second hand cars' fuel type are benzin or diesel (as expected) but hybrid, elektro, cng stands for emergence of new trends in the second-hand car market.



# Bivariate Plots Section

```{r}
set.seed(20022012)
mydata <- data[sample(1:length(data$price), 10000), ]
myvar=c('price', 'kilometer', 'powerPS','yearOfRegistration')
mydata<-mydata[,myvar]
ggpairs(mydata, 
        lower = list(continuous = wrap("points", shape = I('.'))), 
        upper = list(combo = wrap("box", outlier.shape = I('.'))))

```



as we can see form the table, the corrolation between powerPS and Price is stronger than others. and also there is prity good corrolation number between price and kilometer


```{r echo=FALSE, Bivariate_Plots}
ggplot(data=data,aes(x=yearOfRegistration, y=price))+
  geom_point(fill=I("#F79420"),color=I('black'),shape=21)+
  labs(title='Price & Registration Year')+
  geom_smooth()
```


I was expecting that new cars would have the high price but some of the cars even they are quite antique still have high price. those might be special cars such as classics. 

```{r}
ggplot(data=subset(data,(powerPS!=0)&(powerPS<1000) ),
       aes(x=powerPS, y=price))+
  geom_point(fill=I("#F79420"),color=I('black'),shape=21)+
  labs(title='Price & PowerPW')+
  geom_smooth(method = 'lm')+
  coord_flip()
```



the relationship between this are very clear as expected. cars with high horse power are most of the time expensive cars. 


```{r}
ggplot(data=data,aes(y=kilometer, x=price))+
  geom_jitter(fill=I("#F79420"),
              color=I('black'),shape=21)+
  labs(title='Price & kilometer')+
  geom_smooth()
```



I was expecting that when the kilometer is low, pice would be high. but again some cars behave differently. and again those car might be classics. to understand this situation we need to add another veriable. 

```{r}
ggplot(data=data ,
       aes(x=powerPS, y=kilometer))+
  geom_jitter(fill=I("#F79420"),color=I('black'),alpha=0.5, shape=21)+
  labs(title='kilometer & PowerPW')
```
as we can see horse power biger cars more likely to go more kilometer or they try to sell it on more kilometer. 

```{r}
ggplot(data,aes(x=vehicleType, y=price)) +
  geom_boxplot(aes(fill = vehicleType)) +
  stat_summary(fun.y = mean, geom="point", size=2) +
  xlab('Vehicle Type') +
  ylab('Price') +
  ggtitle('Price vs. Vehicle Type')
       
```

We observe that SUV is the most expensive vehicle type while kleinwagen is the cheapest. However, kleinwagen have many outliers which may signify either user error or specific higher end brand and model combination.


```{r}
data<-subset(data, price<20000)
data<-subset(data,powerPS<400)
ggplot(data = subset(data, !is.na(powerPS)), aes(x = powerPS, y = price)) +
  geom_point(alpha = 1/50, color = I("#990000"), position = 'jitter') +
  geom_smooth() +
  facet_wrap(~vehicleType) +
  xlab('Engine Power') +
  ylab('Price') +
  ggtitle('Engine Power vs. Price')
```
There is linear correlation between engine power (PowerPS) and price in each vehicle type but after 150 powerPS it is possible to observe non-linarites.

```{r}
ggplot(aes(x= gearbox, y=price), data=subset(data, gearbox!="")) +
  geom_boxplot(aes(fill=gearbox), color='black') +
  stat_summary(fun.y = mean, geom="point", size=2) +
  labs(x= 'Gearbox', y= 'Price', title= 'Price vs. Gearbox')
```
As expected, the second-hand cars with automatic gearbox are more expensive than manual ones.

# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

ggplot(aes(x=price, y=kilometer,color=gearbox), 
       data = subset(data, gearbox!="") ) + 
  geom_point(alpha=0.5,size=1,position = 'jitter') +
  scale_color_brewer(type='qual', 
                     guide=guide_legend(title = 'Gearbox',reverse=TRUE, 
                                        override.aes = list(alpha=1,size=2)))


```


  
as we can see in lower costs purple is more intense. So manuel cars are more likely to be cheaper. but for range (2500 to 5000) outomatic cars has the lead. but after arout 50000 the both gearbox type has same behavior.


```{r}
ggplot(aes(x=price, y=kilometer,color=vehicleType), 
       data = subset(data, vehicleType!="") ) + 
  geom_smooth(method = 'auto') +
  scale_color_brewer(type='div', 
                     guide=guide_legend(title = 'Vehicle Types',
                                        reverse=TRUE, 
                                        override.aes = list(alpha=1,size=2)))
```


    
kleinwagen model cars are small and has small engine. so that It is not a suprise that they are cheap. also the andre is german word for other. So there is a lot of car models can be in that category. it is hard to trust that line since we dont know what kind a car it is. 

```{r}

ggplot(aes(x=price, y=kilometer,color=fuelType), 
       data = subset(data, fuelType!="") ) + 
  geom_point(size=1,position = 'jitter') +
  scale_color_brewer(type='qual', 
                     guide=guide_legend(title = 'fuel type',
                                        reverse=TRUE, 
                                        override.aes = list(alpha=1,size=2)))

```

```{r}
ggplot(aes(x= fuelType, y= price), data= subset(data, fuelType!="")) +
  geom_boxplot(aes(fill= fuelType), color= 'black') +
  stat_summary(fun.y = mean, geom="point", size=2) +
  labs(x= 'Fuel Type', y='Price', title= 'Price vs. Fuel Type by Vehichle Type') +
  facet_wrap(~vehicleType)

```

------

# Final Plots and Summary

## Plot One

```{r echo=FALSE, Plot_Two}
ggplot(aes(x= gearbox, y=price), data=subset(data, gearbox!="")) +
  geom_boxplot(aes(fill=gearbox), color='black') +
  stat_summary(fun.y = mean, geom="point", size=2) +
  labs(x= 'Gearbox', y= 'Price', title= 'Price vs. Gearbox')

```

### Description One
As expected, the second-hand cars with automatic gearbox are more expensive than manual ones.


## Plot Two
```{r}
ggplot(data = subset(data, powerPS<400), aes(x = powerPS, y = price)) +
  geom_point(alpha = 1/50, color = I("#990000"), position = 'jitter') +
  geom_smooth() +
  facet_wrap(~vehicleType) +
  xlab('Engine Power') +
  ylab('Price') +
  ggtitle('Engine Power vs. Price')
```

### Description Two

There is linear correlation between engine power (PowerPS) and price in each vehicle type but after 150 powerPS it is possible to observe non-linarites.

## Plot tree

```{r}
ggplot(data,aes(x=vehicleType, y=price)) +
  geom_boxplot(aes(fill = vehicleType)) +
  stat_summary(fun.y = mean, geom="point", size=2) +
  xlab('Vehicle Type') +
  ylab('Price') +
  ggtitle('Price vs. Vehicle Type')
```

### Description Three
We observe that SUV is the most expensive vehicle type while kleinwagen is the cheapest. However, kleinwagen have many outliers which may signify either user error or specific higher end brand and model combination.




------

# Reflection

Limousine, kombi and kleinwagen are the most popular vehicle types in the second-hand market. Most expensive cars are SUV's while the cheapest ones are kleinwagens.
On average Kleinwagen vehicle type is the cheapest and has the lowest engine power. But it also shows the most outliers - might be as a result of brand-model diversity.
The most popular brands are Volkswagen, BMW, Opel, Mercedes, Audi, Ford, Renault, Peugeot, Fiat and Seat. These 10 brand correspond to almost 80% of the cars. (Originally our dataset contains around 40 brands)
According to our regression analysis, age (39%), kilometer(%23) and engine power(%19) are the most important factors explaining second hand price.
Most of the cars in the second-hand market are above 100.000 km, even 150.000 km. People does not frequently change cars according to our data set.
Majority of the second-hand cars are sold only within 35 days. The ratio of the first 10 days (day 0 stands for same day sale) is quite high. This shows us that either Ebay-Kleinanzeigen is very successful at targeting customers or the second-hand market is more fluid that we actually thought.
To our surprise, there is no strong/significant correlation between selling time and vehicle type, kilometer and price. We saw that whenever price goes up the change to be sold in 10-20 days increases especially in SUV vehicles (rather than 0-10 days) but this is not a general trend.
Hybrid (electro engine, CNG) second-hand car market is emerging but shows longer selling time trend.

## Personal Reflections
Personaly I have hard time because the data was about Germany's used car and I am from Turkey and living in USA. So I didn't have any knowledge in German market. but it was a very awesome experience forlearing to know very little and figuring out from the raw data.
